Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-15 ms.tex
minor clean-up of MCMC sampling procedure description

For each pixel, we initialize the Markov chain with parameters 
$\tilde{I}_{545}$ = $I_{545}$ and $T_2$ consistent with the FDS99 
DIRBE 100$\mu$m/240$\mu$m ratio map $\mathscr{R}$. The initial proposal 
distribution is a two-dimensional normal distribution, with 
$\sigma_{T_2}$=0.25 K and 
$\sigma_{\tilde{I}_{545}}$=max(0.01$\times$$I_{545}$, 0.05 MJy/sr). We run 5 
iterations of burn-in, each consisting of 500 MH steps. After each burn-in 
iteration, we rescale the proposal distribution so as to ultimately attain an 
acceptance fraction $f_{acc}$ as close as possible to the optimal value 
$f_{opt}=0.234$. This is accomplished by multiplying the proposal distribution 
standard deviations by $f_{acc}$/$f_{opt}$.

We then estimate the parameters and their uncertainties by performing 10,000 
sampling steps, with $T_{2, j}$ and $\tilde{I}_{545, j}$ denoting the proposed 
parameter values at the $j^{th}$ step since the end of burn-in. From these 
10,000 samples, we compute estimates of each parameter's mean, 
$\langle T_2 \rangle$ = $\langle T_{2, j} \rangle$, 
$\langle \tilde{I}_{545} \rangle$ = $\langle \tilde{I}_{545, j} \rangle$, of 
each parameter's variance, 
$\sigma^2_{T_2}$ = $\langle T^2_{2, j} \rangle-\langle T_{2, j} \rangle ^2$, 
$\sigma^2_{\tilde{I}_{545}}$=$\langle \tilde{I}^2_{545, j} 
\rangle-\langle \tilde{I}_{545, j} \rangle ^2$ and of the covariance 
$\sigma_{T_2}\sigma_{\tilde{I}_{545}}$=$\langle T_{2,j}-\langle T_2 \rangle 
\rangle \langle \tilde{I}_{545, j} - \langle \tilde{I}_{545} \rangle \rangle$.

@@

%in the above need to mention/introduce the use of ``j'' to denothe the j'th
%step of the MH sampling **after** burn-in has finished

% actually we I think we want to keep track of $\tilde{I}_{545}$/b_{545}
% which is the monochromatic value, since that is most useful downstream
% when making foreground predictions that typically won't have anything
% to do with Planck bandpasses

>>>>

For each pixel, we initialize the Markov chain with parameters 
$\tilde{I}_{545}$ = $I_{545}$ and $T_2$ consistent with the FDS99 
DIRBE 100$\mu$m/240$\mu$m ratio map $\mathscr{R}$. The initial proposal 
distribution is a two-dimensional normal distribution, with 
$\sigma_{T_2}$=0.25 K, 
$\sigma_{\tilde{I}_{545}}$=max(0.01$\times$$I_{545}$, 0.05 MJy/sr) and
$\sigma_{T_2}\sigma_{\tilde{I}_{545}}$=0. We run 5 iterations of burn-in, each 
consisting of 500 MH steps. After each burn-in iteration, we rescale the 
proposal distribution so as to ultimately attain an acceptance fraction 
$f_{acc}$ as close as possible to the optimal value $f_{opt}=0.234$. This is 
accomplished by multiplying the proposal distribution standard deviations by 
$f_{acc}$/$f_{opt}$.

After burn-in, we estimate the parameters and their uncertainties by performing
10,000 sampling steps, with $T_{2, j}$ and $\tilde{I}_{545, j}$ denoting the 
proposed parameter values at the $j^{th}$ step since the end of burn-in. From 
these 10,000 samples, we compute estimates of each parameter's mean, 
$\langle T_2 \rangle$ = $\langle T_{2, j} \rangle$, 
$\langle \tilde{I}_{545} \rangle$ = $\langle \tilde{I}_{545, j} \rangle$, of 
each parameter's variance, 
$\sigma^2_{T_2}$ = $\langle T^2_{2, j} \rangle-\langle T_{2, j} \rangle ^2$, 
$\sigma^2_{\tilde{I}_{545}}$=$\langle \tilde{I}^2_{545, j} 
\rangle-\langle \tilde{I}_{545, j} \rangle ^2$ and of the covariance 
$\sigma_{T_2}\sigma_{\tilde{I}_{545}}$=$\langle T_{2,j}-\langle T_2 \rangle 
\rangle \langle \tilde{I}_{545, j} - \langle \tilde{I}_{545} \rangle \rangle$.

@@
